{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-15 paper.tex
Expand why ROS not suitable for geometric data

Traditional robotic middlewares, like ROS, are not particularly well-suited to
deal with these different needs: full geometric data can be represented, but are
not first-class citizens (a basic task like displaying a 3D mesh at an arbitrary
position is not particularly easy to perform with ROS) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.

>>>>

Traditional robotic middlewares, like ROS, are not particularly well-suited to
deal with these different needs: full geometric data can be represented, but is
not first-class citizen (a basic task like displaying a 3D mesh at an arbitrary
position is not particularly easy to perform with ROS, requiring the combination
of static Collada meshes, a URDF kinematic description, TF broadcasters, and a
3D visualisation tool like RViz) and critically,
representing and reasoning on alternative states of the environment is not
directly feasible.
